### 2009-12-11 docs/marcello-dissertation/thesis/preamble.tex
Revision of Prof. Puder's audio feedback of chapter 5, as well as entire restructure of the document, such as using more page width and height, making it more visual. Table references not working automatically, as well as page numbers (will review later). Table references are entered manually in the text.
The structure of chapter 5 changed according to the fact that some
sections, subsections were very short, with 1 paragraph. So, I decided
to use two different options:

* If there are more to be discussed, a new advantages/disadvantages
subsection is created; or else, one section includes two

\hoffset=.5in 
\oddsidemargin=0in
\evensidemargin=0in
\topmargin=0.1in 
\headheight=0in
\headsep=1in
\footskip=.8in
\textwidth=5.9in
\textheight=7in

@@

$\mbox{}$
\vspace{3in}
\begin{center}
\singlespace{
    Copyright \copyright{} \thisyear by \myname

    \bigskip

    All rights reserved. No part of the material protected by this
    copyright notice may be reproduced or utilized in any form or by any
    means, electronic or mechanical, including photocopying, recording or
    by any information storage and retrieval system, without the prior
    permission of the author.
}
\end{center}

@@

%\doublespacing{\noindent
\onehalfspacing{\noindent      
Sensor Networks are becoming more and more important to different science
communities bacause of what they produce: the raw data for different studies.
In order to make use the collected data, researchers may have to dissect the
characteristics of the sensor network in question, regarding different
properties such as the purpose and location of the observed data, as well as
how the data is described. For this reason, this work proposes a set of data
persistence taxonomies based on the state of the art, which can be used to
classify the properties of the produced raw data. In order to evaluate the
proposed taxonomies, this work designs and implements a data persistence
component for NetBEAMS, our case study of modular sensor network infrastructure
developed to improve the operation of the SF-BEAMS environmental sensor
network. In this way, based on empirical analysis regarding proposed
taxonomies for the case study, this work selected mongoDB, a schema-less
document-oriented database instead of the traditional use of relational
databases. As a result based on the experiments conducted, this work suggests
that use of Key-Value Pair datasents in orde tor provide External of
Data-Centric approach. Therefore, the use of a solution of the help decreasing
the complexity related to the data persistence layer for sensor networks with
external or data-centric storage mechanism, and whose purpose is data
archival. Finally, this work proposes different future works such a
data-centric approach using Databa se Shards to store te collected data and Map
Reduce to execute parallel queries over the shards.} \vspace*{\fill}

@@

\hrule{\hspace{3.75in}} \\[-10pt]
Chair, Thesis Committee 
\hspace{2.5in}
Date
\doublespacing
\newpage
\[ \]
\vspace{-1.8in}
\begin{center}{ACKNOWLEDGMENTS}\end{center}

>>>>

\pdfpagewidth 8.5in
\pdfpageheight 11in 
\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{0in}
\setlength\textheight{7.7in}
\setlength\textwidth{6.5in}
\setlength\oddsidemargin{0in}
\setlength\evensidemargin{0in}
\setlength\headheight{77pt}
\setlength\headsep{0.25in}

%\hoffset=.5in 
%\oddsidemargin=0in
%\evensidemargin=0in
%\topmargin=0.0in 
%\headheight=0in
%\headsep=1in
%\footskip=.8in
%\textwidth=6.5in
%\textheight=7in

@@

$\mbox{}$
\vspace{3in}
\begin{center}
\singlespace{
    Copyright \copyright{} \thisyear by \myname
%    \bigskip
%    All rights reserved. No part of the material protected by this
%    copyright notice may be reproduced or utilized in any form or by any
%    means, electronic or mechanical, including photocopying, recording or
%    by any information storage and retrieval system, without the prior
%    permission of the author.
}
\end{center}

@@

%\doublespacing{\noindent
\onehalfspacing{\noindent
Sensor Networks are becoming more and more important to different science
communities because of what they produce: the raw data for different domains.
In order to make use the collected data, researchers may have to dissect the
characteristics of the sensor network in question, regarding different
properties such as the purpose and location of the observed data, as well as
how the data is described. For this reason, this work proposes a set of data
persistence taxonomies based on the state of the art, which can be used to
classify the properties of the produced raw data. In order to evaluate the
proposed taxonomies, this work designs and implements a data persistence
component for NetBEAMS, a modular-based sensor network infrastructure
developed to improve the operation of the SF-BEAMS environmental sensor
network. SF-BEAMS is deployed at the Tiburon Island, California, and managed by
the Department of Biology from SFSU. In this way, based on empirical analysis
regarding proposed taxonomies for the case study, this work selected mongoDB,
a schema-less document-oriented database instead of the traditional use of
relational databases. As a result based of the experiments conducted, this
work proposes a novel use of the Key-Value Pair databases in order tor provide
External of Data-Centric approaches. Similarly, this work also agrees to
related literature that the use of programming languages are better abstraction
than the use of traditional query languages used to extract data from Relational
databases, and therefore, it should be the proposed approach to non-technical
researchers such as the Biologists. Finally, this work proposes different
future works such a data-centric approach using Databasese Shards to store the
collected data and Map Reduce to execute parallel queries over distributed
database nodes.} \vspace*{\fill}

@@

\hrule{\hspace{3.75in}} \\[-10pt]
Chair, Thesis Committee 
\hspace{2.5in}
Date
\onehalfspacing
\newpage
\[ \]
\vspace{-1.8in}
\begin{center}{ACKNOWLEDGMENTS}\end{center}
